---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Unzip the _activity.zip_ file in the _data_ folder:

```{r}
zip_file <- "activity.zip"
data_folder <- "data"
if (dir.exists(data_folder)) {
  unlink(data_folder, recursive = TRUE)
}
unzip(zip_file, exdir = data_folder)
```

read the comma-separated-value file named _activity.csv_ from _data_ folder:

```{r}
csv_file <- "activity.csv"
csv_data <- read.csv(file.path(data_folder, csv_file), header = TRUE, sep = ",")
```

change date column:

```{r}
csv_data$date <- as.Date(csv_data$date, "%Y-%m-%d")
```

## What is mean total number of steps taken per day?

For this part of the assignment, we can ignore the missing values in the dataset:

```{r}
csv_data2 <- csv_data[!is.na(csv_data$steps),]
```

and if we tranform date into a factor we won't miss any day that doesn't have data:

```{r}
#%%% csv_data2$date <- factor(csv_data2$date)
#%%% csv_data2$steps[is.na(csv_data2$steps)] <- 0
```

let's group the steps by day and calculate the total number of steps taken per day:

```{r}
steps_day <- with(csv_data2, tapply(steps, date, sum))
head(steps_day)
```

Here's the histogram of the total number of steps taken each day:

```{r}
hist(steps_day, breaks = 10)
```

The mean and median of the total number of steps taken per day is:

```{r}
mean(steps_day)

median(steps_day)

```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
